SST_patterns

### 2019-09-19 SST_patterns.Rmd
Fixed
updated

library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(ncdf4)
library(data.table)
library(plyr)
```

@@

OISST_fil <- filterted_product(df = OISST)
CMC_fil <- filterted_product(df = CMC)

# Next to run upwelling index
```

>>>>

library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(ncdf4)
library(data.table)
library(plyr)
library(heatwaveR)
```

@@

OISST_fil <- filterted_product(df = OISST) # Need to add a site column
CMC_fil <- filterted_product(df = CMC) # Need to add a site column

# OISST_sites <- OISST_fil %>% 
#   left_join(site_list_sub[,c(2,3)], by = c("lat","lon"))

# All the code below can be viewed in upwell_IDX.Rmd
# Next to run upwelling index
# UI Created using SAWS wind data (Find in upwell_IDX_Rmd)
load("Data/UI_angle.RData")

upwelling <- UI_angle %>% 
  dplyr::rename(temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t), 
  #        max_t = max(t)) %>% 
  nest() %>% # apply the following functions to all of the variables in te dataset
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("1997-01-01", "2015-12-31")), # creating a column of climaatologies. Column will be named clim
         # NB: A threshold of 3 appeared to be far to strict
         # purr::map - apllies a function to each element of a vector
         exceed = purrr::map(clim, exceedance, minDuration = 1, threshold = 1)) %>%  #Upwelling cannot be descrbed as an event. Upwelling can last for a few hours. Given that we have daily data, upwelling events minimum duration here will be 1day
  # Detect consecutive days in exceedance of a given threshold.
  # mutate() %>% 
  select(-data, -clim) %>% 
  unnest() %>%
  filter(row_number() %% 2 == 1) %>%
  unnest() %>% # creates a column for each variables
  dplyr::rename(ui.saws = temp) %>% # rename upwelling index vale to temp so that it could work with the function
  select(site, t, ui.saws, exceedance)

# Now applying the Upwelling func
detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 3, coldSpells = T)
  return(res)
}

# Calculate the upwelling event metrics
upwelling_detect_event <- function(df){
upwell_base <- df %>% 
  dplyr::rename(t = date) %>% 
  group_by(lat,lon) %>% 
  nest() %>% 
  # The climatology base period used here is up for debate...
  # The choice of the 30th percentile threshold also needs to be justified and sensitivty tested
  mutate(clim = purrr::map(data, ts2clm, pctile = 25, climatologyPeriod = c("1989-01-01", "2017-12-31"))) %>%
  select(-data) %>% 
  unnest() %>%
  left_join(upwelling, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(lat, lon) %>% 
  # mutate(thresh = mean(seas, na.rm = T)-sd(seas, na.rm = T)) %>% # Manually set threshold to the mean
  # mutate(thresh = 10) %>% # Manually set threshold to a static value. Doesn't work across all sites
  # mutate(thresh = quantile(temp, 0.3, na.rm = T)) %>% # Manually set threshold to a single quantile
  nest() %>% 
  mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  select(-data)
}

OISST_upwell_base <- upwelling_detect_event(df = OISST_fil)
CMC_upwell_base <- upwelling_detect_event(df = CMC_fill)
```
